\documentclass{article}
\usepackage{booktabs}
\usepackage{array}
\usepackage{geometry}
\geometry{margin=1in}

\begin{document}

\section*{Wind Power Forecasting with Gemini 3 Flash}

\subsection*{Table: Complete Results Across Strategies and Horizons}

\begin{table}[h!]
\centering
\caption{Overall Score (kW) for Gemini 3-flash model. Lower is better.}
\label{tab:gemini_results}
\begin{tabular}{lccc}
\toprule
\textbf{Strategy} & \textbf{3-hour} & \textbf{6-hour} & \textbf{48-hour} \\
& (18 points) & (36 points) & (288 points) \\
\midrule
Naive         & & & \\[0.5cm]
Advanced      & & & \\[0.5cm]
APBF          & & & \\[0.5cm]
\midrule
Baseline (GRU) & -- & -- & 315.82 \\
\bottomrule
\end{tabular}
\end{table}

\vspace{0.5cm}

\subsection*{Notes:}
\begin{itemize}
\item \textbf{Overall Score} = (MAE + RMSE) / 2, in kilowatts (kW)
\item Lower scores indicate better forecasting accuracy
\item Fill in each cell with the overall score from your experiments
\item Use ``Failed'' if an experiment couldn't be completed
\item The baseline (GRU) at 48h is 315.82 kW - can any LLM approach beat this?
\end{itemize}

\subsection*{What This Table Shows:}

\textbf{Comparing across columns (same strategy, different horizons):}
\begin{itemize}
\item Which forecast horizon is easiest/hardest?
\item Does error increase as horizon extends (3h → 6h → 48h)?
\end{itemize}

\textbf{Comparing across rows (same horizon, different strategies):}
\begin{itemize}
\item Does Advanced prompting improve over Naive?
\item Does APBF (Advanced + Binning + Forecast) improve over Advanced alone?
\item Which strategy works best for each specific horizon?
\end{itemize}

\textbf{Finding the best configuration:}
\begin{itemize}
\item What is your best result? (lowest score in entire table)
\item Which strategy-horizon combination achieved it?
\end{itemize}

\vspace{1cm}

\subsection*{Example (Our Replication Results):}

\begin{table}[h!]
\centering
\caption{Example: Our replication of your experiments with Gemini 3-flash}
\begin{tabular}{lccc}
\toprule
\textbf{Strategy} & \textbf{3-hour} & \textbf{6-hour} & \textbf{48-hour} \\
\midrule
Naive         & 336.68 & 582.23 & 686.56 \\
Advanced      & 298.92 & 280.28 & 686.56 \\
APBF          & \textbf{144.89} & 211.87 & Failed \\
\midrule
Baseline (GRU) & -- & -- & 315.82 \\
\bottomrule
\end{tabular}
\end{table}

\vspace{0.5cm}

\textbf{Key Observations from Our Replication:}
\begin{itemize}
\item \textbf{Best result:} APBF at 3h = 144.89 kW (beats baseline!)
\item Advanced beats Naive at 3h (298.92 vs 336.68) and 6h (280.28 vs 582.23)
\item APBF dramatically improves short-term forecasts (3h, 6h)
\item APBF 48h failed due to LLM validation issues (couldn't generate exactly 288 values)
\item Shortest horizon (3h) achieves best accuracy
\end{itemize}

\end{document}
