\documentclass{article}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage[table]{xcolor}
\usepackage{geometry}
\geometry{margin=0.75in}

\begin{document}

\section*{Wind Power Forecasting: Complete Results Table}

\begin{table}[h!]
\centering
\caption{Overall Score (kW) for all Model-Strategy-Horizon combinations. Lower is better. Best result in \textbf{bold}.}
\label{tab:complete_results}
\begin{tabular}{llcccc}
\toprule
\multirow{2}{*}{\textbf{Model}} & \multirow{2}{*}{\textbf{Strategy}} & \multicolumn{3}{c}{\textbf{Forecast Horizon}} & \multirow{2}{*}{\textbf{Avg}} \\
\cmidrule{3-5}
& & \textbf{3h} & \textbf{6h} & \textbf{48h} & \\
& & (18 pts) & (36 pts) & (288 pts) & \\
\midrule
\multirow{3}{*}{Gemini 3 Flash}
& Naive    & & & & \\
& Advanced & & & & \\
& APBF     & & & & \\
\cmidrule{2-6}
& \textit{Model Average} & & & & \\
\midrule
\multirow{3}{*}{Gemini 3 Pro}
& Naive    & & & & \\
& Advanced & & & & \\
& APBF     & & & & \\
\cmidrule{2-6}
& \textit{Model Average} & & & & \\
\midrule
\multirow{3}{*}{GPT 5.2}
& Naive    & & & & \\
& Advanced & & & & \\
& APBF     & & & & \\
\cmidrule{2-6}
& \textit{Model Average} & & & & \\
\midrule
\multirow{3}{*}{Claude 3.5 Haiku}
& Naive    & & & & \\
& Advanced & & & & \\
& APBF     & & & & \\
\cmidrule{2-6}
& \textit{Model Average} & & & & \\
\midrule
\multirow{3}{*}{Claude 3.5 Sonnet}
& Naive    & & & & \\
& Advanced & & & & \\
& APBF     & & & & \\
\cmidrule{2-6}
& \textit{Model Average} & & & & \\
\midrule
\midrule
\multicolumn{2}{l}{\textit{Strategy Average - Naive}} & & & & \\
\multicolumn{2}{l}{\textit{Strategy Average - Advanced}} & & & & \\
\multicolumn{2}{l}{\textit{Strategy Average - APBF}} & & & & \\
\midrule
\multicolumn{2}{l}{\textbf{Baseline (GRU)}} & & & 315.82 & \\
\bottomrule
\end{tabular}
\end{table}

\vspace{0.5cm}

\subsection*{Notes:}
\begin{itemize}
\item \textbf{Overall Score} = (MAE + RMSE) / 2, measured in kW
\item Lower scores = better performance
\item Mark the best result in the entire table with \textbf{bold}
\item Use ``--'' for experiments that were not conducted
\item Use ``Failed'' with a footnote for experiments that failed (e.g., $^{\dagger}$)
\item Averages help identify: (1) best model, (2) best strategy, (3) easiest horizon
\end{itemize}

\subsection*{What This Table Reveals:}

\textbf{By comparing across rows (within a model):}
\begin{itemize}
\item Does Advanced prompting beat Naive?
\item Does APBF (Advanced + Binning + Forecast) beat Advanced alone?
\item Which strategy works best for each specific model?
\end{itemize}

\textbf{By comparing across columns (within a strategy):}
\begin{itemize}
\item Which horizon is easiest? (3h typically easier than 48h)
\item Is there a horizon-dependent accuracy trade-off?
\item Do longer horizons consistently degrade performance?
\end{itemize}

\textbf{By comparing model averages:}
\begin{itemize}
\item Which LLM is best for wind forecasting overall?
\item Do larger models (Pro/Sonnet) outperform smaller ones (Flash/Haiku)?
\end{itemize}

\textbf{By comparing strategy averages:}
\begin{itemize}
\item Which prompting technique is most effective across all models?
\item Is the complexity of APBF worth the effort?
\end{itemize}

\textbf{By comparing to baseline:}
\begin{itemize}
\item Do any LLM approaches beat the traditional GRU baseline?
\item Which models/strategies come closest to the baseline?
\end{itemize}

\vspace{0.5cm}

\subsection*{Example of Filled Cell:}

\begin{table}[h!]
\centering
\caption{Example: How to fill one cell}
\begin{tabular}{llc}
\toprule
\textbf{Model} & \textbf{Strategy} & \textbf{3h} \\
\midrule
Gemini 3 Flash & APBF & \textbf{144.89} \\
\bottomrule
\end{tabular}
\end{table}

This shows Gemini 3 Flash with APBF strategy achieved 144.89 kW overall score for 3-hour forecasting (marked bold if it's the best result).

\end{document}
